##### Group member:
#Hengyu Song, s2447118;Yanming Gu, s2304572;Yiqian Dai, s2329960

#Address of github repo:
#https://github.com/syh823/projrct2.git

#Each group member took active participate in the group work.
#Hengyu Gu...
#
#Yanming Gu...
#
#Yiqian Dai...
#
#Each undertake about % of the work...

```{r cars}
 Pone <- function(n, k, strategy, nreps) {
#m is the total number of cards     
     m=2*n
#For strategy 1
     if(strategy==1) {
#Denote sum1 as the number of successful trails that find their prisoner number using strategy1
       sum1=0
       temp=array()
#Repeat replicate simulations (nreps) times 
       for(i in (1:nreps)){
#Generate a random permutation of the elements of 1 to m with length m
         card<-sample(c(1:m),m,replace = FALSE)
#Refers to card number in the box of prisoner number k when prisoner first time open the box 
         temp[1]=card[k]
#Prisoner open box n times
         for(j in (1:n)){
#Prisoner found the card with their number on it when he/she jth time open the box
           if(temp[j]==k)
           {
#The success trials increase by 1
             sum1=sum1+1
             break
           }
           else
           {
#Otherwise, prisoner continues to open the box of the card number in the preious box
               temp[j+1]=card[temp[j]]
           }
         }
         
       }
#The probability of strategy1 is the ratio of successful trials to nrep trails
       prob1=sum1/nreps
       print(prob1)
     }
#For strategy 2
     if(strategy==2) {
#Denote sum2 as the number of successful trails that find their prisoner number using strategy2
     sum2=0
#Repeat replicate simulations (nreps) times
     for (i in (1:nreps)){
        temp2=array()
#Generate a random permutation of the elements of 1 to m with length m
        card<-sample(c(1:m),m,replace = FALSE)
#Prisoner start to open the box of the number randomly selected from 1 to m
        start=sample(c(1:m),1,replace = FALSE)
#Refers to card number in the first box 
        temp2[1]=card[start]
#Prisoner open box n times
        for(j in (1:n)){
#Prisoner found the card with their number on it in the jth box
          if(temp2[j]==k){
#The success trials increase by 1
            sum2=sum2+1
            break
          }
          else{
#Otherwise, prisoner continues to open the box of the card number in the preious box
            temp2[j+1]=card[temp2[j]]
          }
        } 
     }
#The probability of strategy2 is the ratio of successful trials to nrep trails
     prob2=sum2/nreps
     print(prob2)
     }
#For strategy 3
     if(strategy==3) {
#Denote sum3 as the number of successful trails that find their prisoner number using strategy3
      sum3=0 
#Prisoner open box n times
      for(i in (1:nreps)){
#Generate a random permutation of the elements of 1 to m with length n
         temp3=sample(c(1:m),n,replace = FALSE)
#There exist card number same as prisoner number in the n boxes
         if(length(which(temp3==k))!=0){
#The success trials increase by 1
          sum3=sum3+1
         }
      }
#The probability of strategy3 is the ratio of successful trials to nrep trails
      prob3=sum3/nreps
      prob3
    }
     
 }
 #Pone(10,10,1,10000)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
Pall <- function(n, strategy, nreps) {
  m=2*n
  sum=nreps #总成功次数
  if(strategy==1){
    for(i in (1:nreps)){
    card<-sample(c(1:m),m,replace = FALSE)
    for(j in (1:n)){
      account=1
      card_number=j
      while(account<=n){
        card_number=card[card_number]
        if(card_number==j){
          break
        }
        account=account+1
      }
      if(account==n+1){
        sum=sum-1
        break
      }
    }
  }
  print(sum)
  print(sum/nreps)
  }
  if(strategy==2){
    for(i in (1:nreps)){
    card<-sample(c(1:m),m,replace = FALSE)
    for(j in (1:n)){
      account=1
      card_number=sample(c(1:m),1,replace=FALSE)
      while(account<=n){
        card_number=card[card_number]
        if(card_number==j){
          break
        }
        account=account+1
      }
      if(account==n+1){
        sum=sum-1
        break
      }
    }
  }
  print(sum)
  print(sum/nreps)
  }
   if(strategy==3){
    for(i in (1:nreps)){
    card<-sample(c(1:m),m,replace = FALSE)
    for(j in (1:n)){
      card1=card
      account=1
      while(account<=n){
        card_number=sample(card1,1,replace = FALSE)
        card1=card1[-which(card1==card_number)]
        if(card_number==j){
          break
        }
        account=account+1
      }
      if(account==n+1){
        sum=sum-1
        break
      }
    }
  }
  print(sum)
  print(sum/nreps)
  }
  
  
  
}
```
```{r}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.